Assignment 2

### 2025-03-14 code/Reddit_eda.qmd
Added interpretations to analysis graphs

```{r}
# posts data
reddit_posts <- read_xlsx(
  # "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx") |> path for Kevin
  "~/Desktop/UMICH/SURV622_Assignment/data/posts_data_clean.xlsx") |> # path for Felix
  mutate(date_utc = ymd(date_utc)) |> 
  # remove variables not needed
  select(-timestamp)

# comments data
reddit_comment <- read_xlsx(
  # "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx") |> Kevin's path
  "~/Desktop/UMICH/SURV622_Assignment/data/comments_data_clean.xlsx") |> # Felix's path
    mutate(date_utc = ymd(date_utc)) |> 
  # great unique post id
  arrange(date_utc) |> 
  group_by(url) |> 
  mutate(post_id = cur_group_id()) |> 
  ungroup() |> 
  # remove variables not needed
  select(-author, -timestamp, -comment_id)

@@

How many posts were collected in total and by day? How many posts after data cleaning? Is there a pattern with respect to the time of day or day of week when posts were created?
```{r}
# number of total posts
totalposts <- reddit_posts %>%
  summarize(
    TotalPosts = n()
  )
knitr::kable(totalposts)

# number of posts by day
byday <- reddit_posts %>%
  group_by(date_utc) %>%
  summarize(
    total = n()
  )

# plot
ggplot(byday, aes(x = date_utc, y = total)) + 
  geom_point(color = "blue", size = 3) +  # Larger points for visibility
  geom_line(color = "steelblue", linewidth = 1) +  # Thicker line for clarity
  labs(
    title = "Total Number of Posts per Day",
    x = "Day",
    y = "Total Number of Posts"
  ) +
  theme_minimal()

Is there a relationship between events and frequency of tweets?

The two peaks in our graph can potentially be attributed to these two major news stories on those days. On March 5, Elon talked about how he wishes to "save Western civilization from empathy". On March 6, President Trump was reported to further limit Elon Musk's authority amid backlash to DOGE cuts. These two events may have had a major impact in the number of Reddit posts related to DOGE and Elon.

What are the words in the set of posts you have assembled that appear most frequently? 
```{r}
# tokenize words to count frequencies for reddit posts
posts_word_counts <- reddit_posts |>
  select(title, text) |>
  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 50)

@@

The above graphs show the most frequent words in both reddit posts and their comments. Most of these are stopwords, therefore we will proceed to remove these to get a better idea of what people are really discussing.

How does this change if you exclude “stop words” such as “a,” “an,” “the,” “is,” and others that are common in English sentences but are generally not informative?
```{r}
# tokenize words to count frequencies for reddit posts removing stop words
posts_word_counts <- reddit_posts |>
  select(title, text) |>
  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 50)

@@

The above graphs show the most frequent words used in both Reddit posts and their comment sections. We see that most of these are directly related to our topic, with mentions of the President, DOGE, the federal government and RIF.

>>>>

```{r}
# posts data
reddit_posts <- read_xlsx(
  # "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx") |> path for Kevin
  "~/Desktop/UMICH/SURV622_Assignment/data/posts_data_clean.xlsx") |> # path for Felix
  mutate(date_utc = ymd(date_utc)) |> 
  # remove variables not needed
  # select(-timestamp)
  mutate(
    # Convert timestamp to POSIXct format
    timestamp = as.POSIXct(timestamp, origin = "1970-01-01", tz = "UTC"),

    # Extract time of day (you can adjust the format as needed)
    time_of_day = format(timestamp, "%H:%M:%S")
  )

# comments data
reddit_comment <- read_xlsx(
  # "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx") |> Kevin's path
  "~/Desktop/UMICH/SURV622_Assignment/data/comments_data_clean.xlsx") |> # Felix's path
    mutate(date_utc = ymd(date_utc)) |> 
  # great unique post id
  arrange(date_utc) |> 
  group_by(url) |> 
  mutate(post_id = cur_group_id()) |> 
  ungroup() |> 
  # remove variables not needed
  mutate(
    # Convert timestamp to POSIXct format
    timestamp = as.POSIXct(timestamp, origin = "1970-01-01", tz = "UTC"),

    # Extract time of day (you can adjust the format as needed)
    time_of_day = format(timestamp, "%H:%M:%S")
  ) |>
  select(-author, -comment_id)

@@

## How many posts were collected in total and by day? How many posts after data cleaning? Is there a pattern with respect to the time of day or day of week when posts were created? Is there a relationship between events and frequency of tweets?
```{r}
# number of total posts
totalposts <- reddit_posts %>%
  summarize(
    TotalPosts = n()
  )
knitr::kable(totalposts)

# number of posts by day
byday_posts <- reddit_posts %>%
  group_by(date_utc) %>%
  summarize(
    total = n()
  )

# plot
ggplot(byday_posts, aes(x = date_utc, y = total)) + 
  geom_point(color = "blue", size = 3) +  
  geom_line(color = "steelblue", linewidth = 1) +  
  labs(
    title = "Total Number of Posts per Day",
    x = "Day",
    y = "Total Number of Posts"
  ) +
  theme_minimal()

# number of total comments
totalcomments <- reddit_comment %>%
  summarize(
    TotalComments = n()
  )
knitr::kable(totalcomments)

# number of comments by day
byday_comments <- reddit_comment %>%
  group_by(date_utc) %>%
  summarize(
    total = n()
  )

# plot
ggplot(byday_comments, aes(x = date_utc, y = total)) + 
  geom_point(color = "green", size = 3) +  
  geom_line(color = "lightgreen", linewidth = 1) +
  labs(
    title = "Total Number of Posts per Day",
    x = "Day",
    y = "Total Number of Posts"
  ) +
  theme_minimal()
```

There appears to be a noticeable peak in activity during the middle of the week. However, we don't have enough data to conclusively say it's due to the day of the week itself. It's more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.

The two peaks in our graph could be attributed to two major news stories. On March 5, Elon Musk made a statement about wanting to "save Western civilization from empathy," and on March 6, there were reports that President Trump was limiting Musk's authority due to backlash over cuts to DOGE. These events likely had a significant impact on the volume of Reddit posts related to Elon Musk and DOGE, driving the observed spikes in activity.

```{r}
# Number of posts by time of day (hour)
byhour_posts <- reddit_posts %>%
  mutate(hour_of_day = hour(timestamp)) %>%
  group_by(hour_of_day) %>%
  summarize(total = n())

# Plot number of posts by hour of day
ggplot(byhour_posts, aes(x = hour_of_day, y = total)) + 
  # geom_bar(stat = "identity", fill = "steelblue") + 
  geom_point(color = "blue", size = 3) +  
  geom_line(color = "steelblue", linewidth = 1) +
  labs(
    title = "Total Number of Posts by Hour of Day (24-hour clock)",
    x = "Hour of Day",
    y = "Total Number of Posts"
  ) +
  theme_minimal()

# Number of comments by time of day (hour)
byhour_comments <- reddit_comment %>%
  mutate(hour_of_day = hour(timestamp)) %>%
  group_by(hour_of_day) %>%
  summarize(total = n())

# Plot number of posts by hour of day
ggplot(byhour_comments, aes(x = hour_of_day, y = total)) + 
  # geom_bar(stat = "identity", fill = "lightgreen") + 
  geom_point(color = "green", size = 3) +  
  geom_line(color = "lightgreen", linewidth = 1) +
  labs(
    title = "Total Number of Comments by Hour of Day (24-hour clock)",
    x = "Hour of Day",
    y = "Total Number of Posts"
  ) +
  theme_minimal()
```

Most posts occur during the early morning, noon, and afternoon hours. The highest peak is around lunchtime, likely due to people posting during their lunch break. There is also significant activity in the afternoon, evening, and early morning. This could be because people have more free time or stay up late, allowing them to take the time to write posts, which require more effort than quick interactions. The fewest posts are seen in the morning, which makes sense as people are typically getting ready for work, commuting, or sleeping in.

The trend for comments mirrors that of posts. This makes sense because people are likely using Reddit at similar times for both posting and commenting. However, the volume of comments is much higher than the number of posts, as each post receives many comments from different users.

## What are the words in the set of posts you have assembled that appear most frequently? 
```{r}
# tokenize words to count frequencies for reddit posts
posts_word_counts <- reddit_posts |>
  select(title, text) |>
  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 50)

@@

The graphs above show the most frequent words in both Reddit posts and their comments. However, many of these words are stopwords, which don't provide much insight into the actual content of the discussions. To get a better understanding of what people are really talking about, we will remove these stopwords in the next step.

## How does this change if you exclude “stop words” such as “a,” “an,” “the,” “is,” and others that are common in English sentences but are generally not informative?
```{r}
# tokenize words to count frequencies for reddit posts removing stop words
posts_word_counts <- reddit_posts |>
  select(title, text) |>
  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 50)

@@

The graphs above show the most frequent words used in both Reddit posts and their comment sections. We can see that many of these words are directly related to our topic, with frequent mentions of the President, DOGE, the federal government, and RIF.

### 2025-03-14 code/Reddit_eda.tex
Added interpretations to analysis graphs

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# posts data}
\NormalTok{reddit\_posts }\OtherTok{\textless{}{-}} \FunctionTok{read\_xlsx}\NormalTok{(}
  \CommentTok{\# "\textasciitilde{}/repos/SURV622\_Assignment/data/posts\_data\_clean.xlsx") |\textgreater{} path for Kevin}
  \StringTok{"\textasciitilde{}/Desktop/UMICH/SURV622\_Assignment/data/posts\_data\_clean.xlsx"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \CommentTok{\# path for Felix}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date\_utc =} \FunctionTok{ymd}\NormalTok{(date\_utc)) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# remove variables not needed}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{timestamp)}

\CommentTok{\# comments data}
\NormalTok{reddit\_comment }\OtherTok{\textless{}{-}} \FunctionTok{read\_xlsx}\NormalTok{(}
  \CommentTok{\# "\textasciitilde{}/repos/SURV622\_Assignment/data/comments\_data\_clean.xlsx") |\textgreater{} Kevin\textquotesingle{}s path}
  \StringTok{"\textasciitilde{}/Desktop/UMICH/SURV622\_Assignment/data/comments\_data\_clean.xlsx"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \CommentTok{\# Felix\textquotesingle{}s path}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date\_utc =} \FunctionTok{ymd}\NormalTok{(date\_utc)) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# great unique post id}
  \FunctionTok{arrange}\NormalTok{(date\_utc) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{group\_by}\NormalTok{(url) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{post\_id =} \FunctionTok{cur\_group\_id}\NormalTok{()) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{ungroup}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# remove variables not needed}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{author, }\SpecialCharTok{{-}}\NormalTok{timestamp, }\SpecialCharTok{{-}}\NormalTok{comment\_id) }

@@

How many posts were collected in total and by day? How many posts after
data cleaning? Is there a pattern with respect to the time of day or day
of week when posts were created?

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# number of posts by day}
\NormalTok{byday }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(date\_utc) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}
    \AttributeTok{total =} \FunctionTok{n}\NormalTok{()}
\NormalTok{  )}

\CommentTok{\# plot}
\FunctionTok{ggplot}\NormalTok{(byday, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date\_utc, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"blue"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  \CommentTok{\# Larger points for visibility}
  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"steelblue"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}  \CommentTok{\# Thicker line for clarity}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Total Number of Posts per Day"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Day"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

Is there a relationship between events and frequency of tweets?

The two peaks in our graph can potentially be attributed to these two
major news stories on those days. On March 5, Elon talked about how he
wishes to ``save Western civilization from empathy''. On March 6,
President Trump was reported to further limit Elon Musk's authority amid
backlash to DOGE cuts. These two events may have had a major impact in
the number of Reddit posts related to DOGE and Elon.

What are the words in the set of posts you have assembled that appear
most frequently?

@@

The above graphs show the most frequent words in both reddit posts and
their comments. Most of these are stopwords, therefore we will proceed
to remove these to get a better idea of what people are really
discussing.

How does this change if you exclude ``stop words'' such as ``a,''
``an,'' ``the,'' ``is,'' and others that are common in English sentences
but are generally not informative?

@@

@@

The above graphs show the most frequent words used in both Reddit posts
and their comment sections. We see that most of these are directly
related to our topic, with mentions of the President, the federal
government, DOGE and RIF.

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# posts data}
\NormalTok{reddit\_posts }\OtherTok{\textless{}{-}} \FunctionTok{read\_xlsx}\NormalTok{(}
  \CommentTok{\# "\textasciitilde{}/repos/SURV622\_Assignment/data/posts\_data\_clean.xlsx") |\textgreater{} path for Kevin}
  \StringTok{"\textasciitilde{}/Desktop/UMICH/SURV622\_Assignment/data/posts\_data\_clean.xlsx"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \CommentTok{\# path for Felix}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date\_utc =} \FunctionTok{ymd}\NormalTok{(date\_utc)) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# remove variables not needed}
  \CommentTok{\# select({-}timestamp)}
  \FunctionTok{mutate}\NormalTok{(}
    \CommentTok{\# Convert timestamp to POSIXct format}
    \AttributeTok{timestamp =} \FunctionTok{as.POSIXct}\NormalTok{(timestamp, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{, }\AttributeTok{tz =} \StringTok{"UTC"}\NormalTok{),}

    \CommentTok{\# Extract time of day (you can adjust the format as needed)}
    \AttributeTok{time\_of\_day =} \FunctionTok{format}\NormalTok{(timestamp, }\StringTok{"\%H:\%M:\%S"}\NormalTok{)}
\NormalTok{  )}

\CommentTok{\# comments data}
\NormalTok{reddit\_comment }\OtherTok{\textless{}{-}} \FunctionTok{read\_xlsx}\NormalTok{(}
  \CommentTok{\# "\textasciitilde{}/repos/SURV622\_Assignment/data/comments\_data\_clean.xlsx") |\textgreater{} Kevin\textquotesingle{}s path}
  \StringTok{"\textasciitilde{}/Desktop/UMICH/SURV622\_Assignment/data/comments\_data\_clean.xlsx"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \CommentTok{\# Felix\textquotesingle{}s path}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date\_utc =} \FunctionTok{ymd}\NormalTok{(date\_utc)) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# great unique post id}
  \FunctionTok{arrange}\NormalTok{(date\_utc) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{group\_by}\NormalTok{(url) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{post\_id =} \FunctionTok{cur\_group\_id}\NormalTok{()) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{ungroup}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# remove variables not needed}
  \FunctionTok{mutate}\NormalTok{(}
    \CommentTok{\# Convert timestamp to POSIXct format}
    \AttributeTok{timestamp =} \FunctionTok{as.POSIXct}\NormalTok{(timestamp, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{, }\AttributeTok{tz =} \StringTok{"UTC"}\NormalTok{),}

    \CommentTok{\# Extract time of day (you can adjust the format as needed)}
    \AttributeTok{time\_of\_day =} \FunctionTok{format}\NormalTok{(timestamp, }\StringTok{"\%H:\%M:\%S"}\NormalTok{)}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{author, }\SpecialCharTok{{-}}\NormalTok{comment\_id) }

@@

\subsection{How many posts were collected in total and by day? How many
posts after data cleaning? Is there a pattern with respect to the time
of day or day of week when posts were created? Is there a relationship
between events and frequency of
tweets?}\label{how-many-posts-were-collected-in-total-and-by-day-how-many-posts-after-data-cleaning-is-there-a-pattern-with-respect-to-the-time-of-day-or-day-of-week-when-posts-were-created-is-there-a-relationship-between-events-and-frequency-of-tweets}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# number of posts by day}
\NormalTok{byday\_posts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(date\_utc) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}
    \AttributeTok{total =} \FunctionTok{n}\NormalTok{()}
\NormalTok{  )}

\CommentTok{\# plot}
\FunctionTok{ggplot}\NormalTok{(byday\_posts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date\_utc, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"blue"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"steelblue"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}  
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Total Number of Posts per Day"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Day"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# number of total comments}
\NormalTok{totalcomments }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}
    \AttributeTok{TotalPosts =} \FunctionTok{n}\NormalTok{()}
\NormalTok{  )}
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(totalcomments)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}r@{}}
\toprule\noalign{}
TotalPosts \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
12492 \\
\end{longtable}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# number of comments by day}
\NormalTok{byday\_comments }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(date\_utc) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}
    \AttributeTok{total =} \FunctionTok{n}\NormalTok{()}
\NormalTok{  )}

\CommentTok{\# plot}
\FunctionTok{ggplot}\NormalTok{(byday\_comments, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date\_utc, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"green"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"lightgreen"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Total Number of Posts per Day"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Day"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-5-2.pdf}

There appears to be a noticeable peak in activity during the middle of
the week. However, we don't have enough data to conclusively say it's
due to the day of the week itself. It's more likely that these spikes
are linked to specific events that occurred on those days, which sparked
conversations.

The two peaks in our graph could be attributed to two major news
stories. On March 5, Elon Musk made a statement about wanting to ``save
Western civilization from empathy,'' and on March 6, there were reports
that President Trump was limiting Musk's authority due to backlash over
cuts to DOGE. These events likely had a significant impact on the volume
of Reddit posts related to Elon Musk and DOGE, driving the observed
spikes in activity.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Number of posts by time of day (hour)}
\NormalTok{byhour\_posts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{hour\_of\_day =} \FunctionTok{hour}\NormalTok{(timestamp)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(hour\_of\_day) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{total =} \FunctionTok{n}\NormalTok{())}

\CommentTok{\# Plot number of posts by hour of day}
\FunctionTok{ggplot}\NormalTok{(byhour\_posts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ hour\_of\_day, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
  \CommentTok{\# geom\_bar(stat = "identity", fill = "steelblue") + }
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"blue"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"steelblue"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Total Number of Posts by Hour of Day (24{-}hour clock)"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Hour of Day"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Number of comments by time of day (hour)}
\NormalTok{byhour\_comments }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{hour\_of\_day =} \FunctionTok{hour}\NormalTok{(timestamp)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(hour\_of\_day) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{total =} \FunctionTok{n}\NormalTok{())}

\CommentTok{\# Plot number of posts by hour of day}
\FunctionTok{ggplot}\NormalTok{(byhour\_comments, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ hour\_of\_day, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
  \CommentTok{\# geom\_bar(stat = "identity", fill = "lightgreen") + }
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"green"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"lightgreen"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Total Number of Comments by Hour of Day (24{-}hour clock)"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Hour of Day"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

Most posts occur during the early morning, noon, and afternoon hours.
The highest peak is around lunchtime, likely due to people posting
during their lunch break. There is also significant activity in the
afternoon, evening, and early morning. This could be because people have
more free time or stay up late, allowing them to take the time to write
posts, which require more effort than quick interactions. The fewest
posts are seen in the morning, which makes sense as people are typically
getting ready for work, commuting, or sleeping in.

The trend for comments mirrors that of posts. This makes sense because
people are likely using Reddit at similar times for both posting and
commenting. However, the volume of comments is much higher than the
number of posts, as each post receives many comments from different
users.

\subsection{What are the words in the set of posts you have assembled
that appear most
frequently?}\label{what-are-the-words-in-the-set-of-posts-you-have-assembled-that-appear-most-frequently}

@@

The graphs above show the most frequent words in both Reddit posts and
their comments. However, many of these words are stopwords, which don't
provide much insight into the actual content of the discussions. To get
a better understanding of what people are really talking about, we will
remove these stopwords in the next step.

\subsection{How does this change if you exclude ``stop words'' such as
``a,'' ``an,'' ``the,'' ``is,'' and others that are common in English
sentences but are generally not
informative?}\label{how-does-this-change-if-you-exclude-stop-words-such-as-a-an-the-is-and-others-that-are-common-in-english-sentences-but-are-generally-not-informative}

@@

\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-8-1.pdf}

@@

\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-8-2.pdf}

The graphs above show the most frequent words used in both Reddit posts
and their comment sections. We can see that many of these words are
directly related to our topic, with frequent mentions of the President,
DOGE, the federal government, and RIF.
